---
title: "Flowchart"
author: "Rachel Havranek"
date: "9/25/2018"
output: html_document
---

I am creating a flowchart for how I want to approach this problem. I took this tact because I would like to learn how to ues Graphviz (in DiagrammeR) so that I can include flowcharts for a paper I am writing that will include a new workflow. 

```{r, message=FALSE}
library(tidyverse)
library(ggplot2)
library(plotly)
library(DiagrammeR)
```
This is the simplest flow chart, using the library mermaid inside DiagrammeR. You open the flow chart with " define which direction the flow chart should proceed and then tell it what connections to make
```{r}
mermaid(" 
  graph TB 
  A-->B
"
)
```

```{r}
mermaid("graph LR; A-->B; A-->C") #You can also put semicolons between the objects and keep it all on one line 
```

Using brackets after the letter tells mermaid what text should be insdie the bubble. [] for square, () for rounded rectangel, (()) for circle, {} for a diamond, >] makes a flag
```{r}
mermaid("
  graph TD
  A[C++ basics]-->B[Note Code]
        ")
```

```{r}
mermaid ("
         graph LR
         A[C++ Basics]-->D[Comment on existing code]
         B[Find examples of existing MFC code]-->D
         C[Hunt down Sierra Instruments specifics]-->E[Use existing code and Sierra specifics to write my own code]
         D-->E
         ")
```

